SSA based global code motion of identical computations

### 2017-04-15 acmart-pacmpl-template.tex
isliveout

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{comment}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{graphviz}
\usepackage{auto-pst-pdf}
\usepackage{etoolbox}
\usepackage{flushend}
\usepackage{needspace}

@@

We compute merge sets of the control flow graph which remains
same through the code-motion transformation. For code-motion we only want to
know if a use operand is a kill (to compute changes in register pressure). For
that we only need to know whether the use is also required later in the
execution path. A variable is live out of a basic block B if it is used in the
merge set of B. We compute the live-out relation on-demand when profitability of
hoistable/sinkable candidates is to be evaluated.

>>>>

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{comment}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{graphviz}
\usepackage{auto-pst-pdf}
\usepackage{etoolbox}
\usepackage{flushend}
\usepackage{needspace}
\usepackage{algpseudocode}

@@

We compute merge sets of the control flow graph which remains same through the
code-motion transformation. For code-motion we only want to know if a use
operand is a kill (to compute changes in register pressure). For that we only
need to know whether the use is also required later in the execution path. A
variable is live out of a basic block B if it is used in the merge set of B. We
compute the live-out relation on-demand when profitability of hoistable/sinkable
candidates is to be evaluated. A simplified version of isLiveOutUsingMergeSet is
presented here:

\begin{verbatim}
  Compute if variable a is liveout from basic block n
  Input: Node N, Variable a

  if a is defined in N then
    if a is used outside any basic block other than N then
      return true;
    else return false;
  endif

  Ms(n) = null;
  // Mergeset of N is the union of merge sets of its successors
  for w in successors(n) do
    Ms(n) = Ms(n) U Mr(w);
  endfor

  // Iterate over all the uses of a and see if any intersect with the
  // merge set of N.
  for t in users(a) do
    b = basic_block(t)
    while (b != null) and (b != def_bb(a)) do
      if b ∩ Ms(n) then
        return true;
      endif
      b = dom-parent(b);
    endwhile
  endfor
  return false;
\end{verbatim}

The original algorithm presented in \cite{das2012} has mismatched types in terms
of uses and nodes because each node can have many uses. Also, while iterating on
the dominator of each user of a variable we may reach to the beginning of a
function, in that case the inner while loop needs to terminate. These two cases
were missing from the algorithm and we came across them during implementation.
